%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Competitions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Hotels.com Winter Hackathon} % Job title
    {Hotels.com} % Organization
    {London, United Kingdom} % Location
    {Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A 24-hour internal hackathon entitled ``Fast on Fones R Us'.}
        \item {Developed and presented a Q\&A bot that consumes Hotels.com's APIs and uses decision trees in order to facilitate hotel search, alongside a team of 7 software developers.}
      \end{cvitems}
    }  
  
  \cventry
    {Google Code Jam 2014} % Job title
    {Google} % Organization
    {Virtual} % Location
    {Apr. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {An international programming competition hosted and administered by Google.}
      \end{cvitems}
    }  
  
  \cventry
    {IEEEXtreme Programming Competition 7.0} % Job title
    {IEEE} % Organization
    {Virtual} % Location
    {Oct. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A global challenge in which teams of IEEE Student members -advised and proctored by an IEEE member, and often supported by an IEEE Student Branch- compete in a 24-hour time span against each other to solve a set of programming problems.}
      \end{cvitems}
    }
    
  \cventry
    {IEEEXtreme Programming Competition 6.0} % Job title
    {IEEE} % Organization
    {Virtual} % Location
    {Oct. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A global challenge in which teams of IEEE Student members -advised and proctored by an IEEE member, and often supported by an IEEE Student Branch- compete in a 24-hour time span against each other to solve a set of programming problems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {``Lysias'' Competition} % Job title
    {Greek Ministry of Education, Research and Religious Affairs} % Organization
    {Virtual} % Location
    {Mar. 2002} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {LYSIAS is an annual Internet-based Panhellenic competition for students. Participants are required to answer 35 standardized questions (multiple choice and True/False, covering a range of school subjects (Mathematics, Physics, Chemistry, Biology, Information Technology, Ancient and Modern Greek, History, Geography, Economics, Art) as well as general knowledge questions.}
        \item {Qualified for final round (top 64 students in Greece).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
