%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Conferences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {European Joint Conferences on Theory and Practice of Software  (ETAPS)} % Job title
    {Easy Conferences} % Organization
    {Thessaloniki, Greece} % Location
    {Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {ETAPS is the primary European forum for academic and industrial researchers working on topics relating to Software Science. It is a confederation of five main annual conferences (ESOP, FASE, FOSSACS, POST and TACAS) accompanied by satellite workshops and other events.}
        \item {I participated at FASE conference where I presented the paper entitled ``Summarizing Software API Usage Examples using Clustering Techniques''. The paper proposes a novel approach for mining API usage examples from client source code, which lies between two popular mining methods, snippet and sequence mining.}
      \end{cvitems}
    }

  \cventry
    {Voxxed Days Thessaloniki} % Job title
    {SoftConf} % Organization
    {Thessaloniki, Greece} % Location
    {Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A two-day conference that brings together popular speakers, core developers of popular open source technologies and professionals willing to share their knowledge and experiences.}
      \end{cvitems}
    }
    
   \cventry
    {EI Global Cloud xTech Conference} % Job title
    {Expedia Inc.} % Organization
    {London, UK} % Location
    {Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A two-day internal conference featuring industry keynote speakers, panels and presentations from colleagues and special guests focusing on Cloud technologies used at Expedia Inc.}
      \end{cvitems}
    }

  \cventry
    {Devoxx UK} % Job title
    {Dmje Lt} % Organization
    {London, UK} % Location
    {May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Devoxx is a two-day annual conference that welcomes over 11,000 developers to events in Belgium, France, UK, Poland, Morocco \& the USA. Attended several sessions, mainly related to the Java Language, Architecture,  Cloud, Big Data \& Machine Learning.}
      \end{cvitems}
    }

  \cventry
    {7\textsuperscript{th} Panhellenic Electrical and Computer Engineering Students Conference} % Job title
    {Aristotle University of Thessaloniki} % Organization
    {Thessaloniki, Greece} % Location
    {Apr. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A three-day conference which aims to gather every Electrical and Computer Engineering student from around Greece and give insight into the latest technological breakthroughs and the new challenges of the market. The conference, entitled ``Dismantling the Problem: The Engineers of the Modern Days'' included talks as well as technical sessions.}
        \item {Successfully organised a programming contest as part of ``Auth Programming Contests'' in the last day of the conference. The competition attracted more than 30 students.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
