%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Associate Software Dev Engineer} % Job title
    {Hotels.com (Expedia Inc.)} % Organization
    {London, United Kingdom} % Location
    {Sep. 2016 - PRESENT} % Date(s)
    {
    \textit{Team specific}:
    \vspace{12pt}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Part of Customer Retention Team (CRT), which is responsible for designing and building technical solutions on how customers are identified, sign up for an account, and sign in to their account.}
        \item {Contributed to most of the key projects of the team including the redesigned ``Forgot Password'' flow and the ``Password-less Sign-in'' flow, as well as to several security-related investigations.}
        \item{Improved monitoring and alerting for our services in Grafana.}
                \item {Using Java/Scala and the Spring MVC, Spring Boot, and Scalatra Frameworks to serve web content.}
        \item {Using Spring MVC Test Framework, Mockito and TestNG for unit testing.}
        \item{Exposed to Cucumber for writing acceptance tests in Java/Scala.}
        \item {Using Docker to automate the deployment of our applications.}
        \item {Using Python to automate everyday tasks and for data manipulation.}
        \item {Using Splunk for log analysis.}
       \item {Using MySQL and Datastax Cassandra NoSQL databases.}
        \item {Following popular Agile practices including Pair Programming, CI, TDD, and BDD.}
        \item {Following the Scrum process and using Atlassian's JIRA Software to support project management.}
        \item {Using Atlassian's software products including Bitbucket Server for version control, Bamboo Server for Continuous Delivery, and Confluence for better team collaboration.}
       \end{cvitems}
       \vspace{15pt}
       \textit{Side projects/activities}:
       \vspace{12pt}
       \begin{cvitems}
        \item {Active part of grads/interns interviews. My responsibilities included writing, reviewing, and testing the coding challenges on Hackerrank as well as interviewing candidates during their final round interviews.}
         \item {Core member of the ``Hacking for Gender Balance'' project, an ongoing project which started as a hackathon project with its main idea being to use Jira to track candidates applications. Among others, I've implemented a Groovy listener on Jira's ScriptRunner that predicts and populates the gender of the candidate based on his/her full name, by communicating with NameApi.}
        \item{Organised several brown bag sessions where I introduced new technologies and tools that I have built as part of our innovation time.}
        \item{Successfully conducted a pilot user survey for \textit{CLAMS}, the system that I developed as part of my MSc project and which I applied to Hotels.com's source code (see \textit{Personal Projects} section).}
         \item{Have been working on several different projects as part of our innovation time, including but no limited to PoCs to improve or replace the internal code search engine tools available at Hotels.com, or getting exposed to the AWS ecosystem.}
      \end{cvitems}
    }
\vspace{100pt}
%---------------------------------------------------------
\end{cventries}