%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Seminars}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Microservices Day London} % Job title
    {nearForm Ltd.} % Organization
    {London, United Kingdom} % Location
    {May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A one-day, single-track, non-profit event that focuses on the evolution and transformation of enterprise from a technology perspective. The day included, among others, talks about the pros and cons of Microservices, popular Microservices Architectures, and the approach for moving from monoliths to Microservices.}
      \end{cvitems}
    }

  \cventry
    {AWSome Day} % Job title
    {Amazon} % Organization
    {London, United Kingdom} % Location
    {Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A one-day training event delivered by AWS technical instructors. The day included a session highlighting why customers are using AWS to develop, deploy and operate secure applications and IT services, as well as technical sessions that covered the AWS foundational services such as Amazon EC2, Amazon S3 and Amazon RDS.}
      \end{cvitems}
    }
    
  \cventry
    {Data Analytics with MATLAB} % Job title
    {MathWorks} % Organization
    {Edinburgh, United Kingdom} % Location
    {Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {During this seminar experienced MathWorks engineers presented how MATLAB can be used to accelerate algorithm development and exploration, and reduce development time for machine learning, image processing and computer vision applications, using live application examples.}
      \end{cvitems}
    }
    
  \cventry
    {Google Developer Days CodeLab on the new DART Language} % Job title
    {GDG Thessaloniki} % Organization
    {Thessaloniki, Greece} % Location
    {Feb. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Two-day event organised by Google Developers Group Thessaloniki which included tech talks as well as workshops on the DART language.}
      \end{cvitems}
    }
    
%  \cventry
%    {Web and Mobile app Development} % Job title
%    {Aristotle University of Thessaloniki} % Organization
%    {Thessaloniki, Greece} % Location
%    {Sep. 2011 - Mar 2012} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {A 40-hour seminar covering technologies including, among others, HTML, CSS, JavaScript, PHP, and MySQL. }
%        \item {Developed a board game website for tichu players.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
