%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Volunteering}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Teaching Assistant (TA) at Expedia Codeacademy ``Python Level 2'' course} % Job title
    {Expedia Inc.} % Organization
    {London, United Kingdom} % Location
    {Jan. 2017 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Providing classroom support by answering questions, resolving technical issues, and guiding students to complete their assignments in Python.}
        \item {Supporting drop-in sessions.}
        \item {Providing support as well as useful resources through course's Slack channel.}
      \end{cvitems}
    } 
%---------------------------------------------------------
  \cventry
    {Computer Systems Operator (Soldier)} % Job title
    {Greek Army} % Organization
    {Xanthi, Greece} % Location
    {Nov. 2014 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Responsible for the software used to control the targets during tank shots, as well as for many electronic devices that enabled monitoring of the shots.}
      	\item {Drafted tutorials for the electronic devices and the software I used as part of my responsibilities.}
      	\item {Drafted reports about results of the tank shots and about condition of the electronic equipment that was used during tank shots.}
        \item {Updated presentations used to support tank shots.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Organising member at ``Auth Programming Contests''} % Job title
    {Aristotle University of Thessaloniki} % Organization
    {Thessaloniki, Greece} % Location
    {Dec. 2013 - Apr. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I focused on organising online programming contests for undergraduate students at Aristotle University of Thessaloniki (School of Electrical and Computer Engineering)
        }
        \item {Contributed to the website used for the programming competitions (available at \url{http://contests.ee.auth.gr}) by generating programming problems and providing analysis and solutions for the challenges.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
